---
title: "Variable & Category List"
author: "Jyotiraditya Pradhan"
toc: true
format: html
editor: visual
execute: 
  echo: false
  warning: false
  message: false 
---

::: {.callout-note}
-   **Dataset:** [CMIE Consumer Pyramids<sub>dx</sub>](https://consumerpyramidsdx.cmie.com/) - People of India<sub>dx</sub> - Wave 36 (Sep-Dec 2025).

-   Sample is restricted to males with response status "Accepted" and a non-zero sample weight.

-   This is a list of selected variables.

- The full list of variables can be found [here](https://consumerpyramidsdx.cmie.com/kommon/bin/sr.php?kall=wlist).
:::

```{r}
#| output: false
library(tidyverse)
library(DT)
```

```{r}
#| output: false
df <- read_csv("data/cmie/cmie_people_raw/people_of_india_20250901_20251231_R.csv")

df %>% 
      filter(GENDER == "M") %>% 
      filter(R_MEM_WGT_W != 0) %>% 
      filter(RESPONSE_STATUS == "Accepted") -> df
```

```{r}

display_list <- function(variable){
  
  df %>% 
    count(.data[[variable]]) %>% 
    arrange(desc(n)) %>% 
    select(.data[[variable]]) %>% 
    datatable(colnames = NULL)
}
```


## Social Categories 

### Caste Category

```{r}
display_list("CASTE_CATEGORY")
```

### Caste 

```{r}
display_list("CASTE")
```

### Religion

```{r}
display_list("RELIGION")
```

## Education

### Education Level

```{r}
display_list("EDU")
```


### Discipline

For those who have studied over 10th standard.
```{r}
display_list("DISCIPLINE")
```

## Employment

### Employment Status

```{r}
display_list("EMPLOYMENT_STATUS")
```

### Employment Type

```{r}
display_list("TYPE_OF_EMPLOYMENT")
```

### Employment Arrangement

```{r}
display_list("EMPLOYMENT_ARRANGEMENT")
```

### Occupation

```{r}
display_list("OCCUPATION")
```

### Nature of Occupation

```{r}
display_list("NATURE_OF_OCCUPATION")
```

### Industry of Occupation

```{r}
display_list("INDUSTRY_OF_OCCUPATION")
```


### Place of Work

```{r}
display_list("PLACE_OF_WORK")
```
