---
title: "Panel Continuity Matrices"
author: "Jyotiraditya Pradhan"
format: html
toc: true
execute: 
  echo: false
editor: visual
---

::: callout-note
- **Dataset:** [CMIE Consumer Pyramids<sub>dx</sub>](https://consumerpyramidsdx.cmie.com/) - People of India<sub>dx</sub>.

- Sample is restricted to males with response status "Accepted" and a non-zero sample weight.

- Counts are non-weighted.
:::

```{r import_lib}
#| output: false
library(tidyverse)
library(DT)
library(scales)
```

```{r diplay_func}

display_matrix <- function(output_table){

  num_cols <- names(output_table)[-1]  # exclude first column

  # All numeric values flattened
  all_vals <- unlist(output_table[num_cols])

  # Percentile-based palette (domain is 0-1)
  pal <- col_numeric(
    c("#e08276", "#fddbc7", "#d1e5f0", "#67a9cf"),
    domain = c(0, 1)
  )

  # Compute percentile rank for every value
  pct_vals <- rank(all_vals, na.last = "keep") /
    sum(!is.na(all_vals))

  # Reshape back into the original table dimensions
  pct_mat <- matrix(
    pct_vals,
    nrow = nrow(output_table),
    ncol = length(num_cols),
    byrow = FALSE,
    dimnames = list(NULL, num_cols)
  )

  # Create hidden color columns
  for (col in num_cols) {
    output_table[[paste0(col, "_color")]] <- pal(pct_mat[, col])
  }



  output_table %>% 
    mutate(across(where(is.numeric), comma)) %>% 
    datatable( 
      rownames = F,
      extensions = c("FixedHeader", "FixedColumns"),
      options = list(
        pageLength = 40,
        scrollX = TRUE,
        autoWidth = TRUE,
        fixedHeader = TRUE,
        fixedColumns = list(leftColumns = 1),
        columnDefs = lapply(
          seq_along(num_cols),
          function(i) {
            list(
              visible = FALSE,
              targets = ncol(output_table) - length(num_cols) + i - 1
            )
          }
        )
    ),
    callback = JS("
  table.on('mouseenter', 'td', function() {

    var idx = table.cell(this).index();

    // Remove previous highlighting
    $(table.cells().nodes()).removeClass('active-cell');
    $(table.columns().header()).removeClass('highlight');
    $(table.rows().nodes()).find('td:first-child').removeClass('highlight');
    
    // Hovered cell
    $(this).addClass('active-cell');

    // Highlight column header
    $(table.column(idx.column).header()).addClass('highlight');

    // Highlight first-column cell for this row
    $(table.row(idx.row).nodes())
      .find('td:first-child')
      .addClass('highlight');
  });

  table.on('mouseleave', 'tbody', function() {

    $(table.cells().nodes()).removeClass('highlight');
    $(table.columns().header()).removeClass('highlight');
    $(table.rows().nodes()).find('td:first-child').removeClass('highlight');
  });
  ")
    ) %>% 
    formatStyle(
      columns = c(1),
      fontWeight = "bold"
    ) %>% 
    formatStyle(
      columns = num_cols,
      valueColumns = paste0(num_cols, "_color"),
      backgroundColor = JS("value")
    ) 
}
```

```{css}
.highlight {
  background-color: #ffe082 !important;
}

.active-cell {
  font-weight: bold !important;
}
```

## Full Continuity Matrix

This matrix shows the number of observations present in all the waves between the corresponding waves.

```{r full_continuity_matrix}
readRDS("data/eda/2026-06-01_mentor_meeting/panel_continuity_matrix.Rda") |> 
  display_matrix()
```

## Full Continuity Matrix (Excluding COVID Time)

This matrix shows the number of observations present in all the waves between the corresponding waves. However, data from 2020 and 2021 has not been considered here to exclude COVID related attrition.

```{r full_continuity_matrix_non_covid}
readRDS("data/eda/2026-06-08_mentor_meeting_02/panel_continuity_matrix_non_covid.Rda") |> 
  display_matrix()
```

## P2P Continuity Matrix

This matrix shows the number of observations present in both corresponding waves.

```{r p2p_continuity_matrix}
readRDS("data/eda/2026-06-08_mentor_meeting_02/panel_continuity_matrix_p2p.Rda") |> 
  display_matrix()
```
